\chapter*{Bibliograf\'ia}
  \addcontentsline{toc}{chapter}{Bibliograf\'ia}

\begin{enumerate}
\item Amaya, J. \textbf{Optimizaci\'on Para Estudiantes de Ingenier\'ia}. Departamento de Ingenier\'ia Matem\'atica, Universidad de Chile, 2010.
\item Apostol, T. \textbf{Calculus vol II}. Wiley, 1969.
\item Belmar, C., Leiva F. \textbf{Curso Completo de Introducci\'on a la Microeconom\'ia}. Departamento de Econom\'ia, Universidad de Chile, 2004.
\item Berge, C. \textbf{Espaces Topologiques: Fonctions Mulivoques}. Dunod, 1959.
\item Bertsekas, D. \textbf{Nonlinear Programming}. Athena Scientific, 1995.
\item Border, K., Aliprantis, C. \textbf{Infinite Dimensional Analysis}. Springer, 2006.
\item Border, K. \textbf{Fixed Point Theorems with Applications to Economics and Game Theory}. Cambridge University Press, 1989.
\item Boyd, S., Vandenberghe, L. \textbf{Convex Optimization}. Cambridge University Press, 2009.
\item Buck, C. \textbf{Advanced Calculus}. Mc Graw-Hill, 1965.
\item Cartan, H. \textbf{C\'alculo Diferencial}. Omega, 1972.
\item Cominetti, R., Jofr\'e A. \textbf{Introducci\'on a la Programaci\'on Matem\'atica}. IV Simposio Chileno de Matem\'atica, 1993. 
\item Fleming, W. \textbf{Funciones de Varias Variables}. CECSA, 1969.
\item Jehle, G. \textbf{Advanced Microeconomic Theory}. Addison Wesley, 2000.
\item Karush, W. \textbf{Minima of Functions of Several Variables with Inequalities as Side Constraints}. M. Sc. Dissertation, Dept. of Mathematics, University of Chicago, 1939.
\item Kolmogorov, A., Fomin, S. \textbf{Introductory Real Analysis}. Dover Publications, 1975.
\item Kopka, H., Daly, P. \textbf{Guide to \LaTeX}. Addison-Wesley, 2003. 
\item Krell, R., Rojas, E., Torres-Mart\'inez, J. \textbf{Apuntes de Microeconom\'ia I: Teor\'ia del Consumidor}. Departamento de Econom\'ia, Universidad de Chile, 2009.
\item Kuhn, H., Tucker, W. \textbf{Nonlinear Programming}. Proceedings of 2nd Berkeley Symposium, University of California Press, 1951.
\item Luenberger, D., Ye, Y. \textbf{Linear and Nonlinear Programming}. Springer, 2008.
\item Mathworks Team. \textbf{Learning Matlab 6 Student Version}. Mathworks, 2001. 
\item Mas Colell, A., Whinston, D., Green, J. \textbf{Microeconomic Theory}. Oxford University Press, 1995.
\item Nocedal, J., Wright S. \textbf{Numerical Optimization}. Springer, 1999.
\item Ok, E. \textbf{Real Analysis with Economic Applications}. Princeton University Press, 2007.
\item Ortiz, C., Varas, S., Vera, J. \textbf{Optimizaci\'on y Modelos Para la Gesti\'on}. Dolmen Ediciones, 2000.
\item Piskunov, N. \textbf{C\'alculo Diferencial e Integral, (vol. I y II)}. Editorial MIR, 1970.
\item Rivera, J. \textbf{Microeconom\'ia II: Apunte de Curso}. Departamento de Econom\'ia, Universidad de Chile, 2008.
\item Rosenlicht, M. \textbf{Introduction to Analysis}. Dover Publications, 1985.
\item Royden, H. \textbf{Real Analysis}. Macmillan Company, 1968.
\item Ruszczy\'nski, A. \textbf{Nonlinear Optimization}. Princeton University Press, 2006.
\item Simon, C., Blume, L. \textbf{Mathematics for Economists}. W.W. Norton \& Company, 1994. 
\item Spivak, M. \textbf{Calculus}. Publish or Perish, 2008.
\item Stewart, J. \textbf{C\'alculo Multivariable}. Thomson Learning, 2006.
\item Takayama, A. \textbf{Mathematical Economics}. Cambridge University Press, 1985.
\item Torres-Mart\'inez, J.P. \textbf{Apuntes de Matem\'atica Para Microeconom\'ia Avanzada}. Departamento de Econom\'ia, Universidad de Chile, 2010.
\item Varian, H. \textbf{Microeconomic Analysis}. W.W Norton \& Company, 1992.
\end{enumerate}